Nonlinear system identification with neural networks for process control

### 2020-09-14 twccc.tex
talk.

\title[Data completion of initial gray box models for process control and optimization]{Data completion of initial gray box models for process control and optimization}
\date{September 15, 2020}
\author[Kumar and Rawlings]{\large Pratyush Kumar and James B. Rawlings}
\institute[UCSB]{
	\begin{minipage}{4in}
		\vspace{-10pt}
		\centering
		\raisebox{-0.1\height}{\includegraphics[width=0.25\textwidth]{UCSB_seal}}
		%\hspace*{.2in}
		%\raisebox{-0.5\height}{\includegraphics[width=0.25\textwidth]{jci_logo}}
	\end{minipage}
	\vspace{10pt}
	\newline
	{\large Department of Chemical Engineering}
	\vspace{10pt}
	\newline
	{\large TWCCC Meeting (Virtual)}}
	%\vspace{10pt}
	%\newline
	%{\large Austin, TX}}

@@

% MPC intro frame
\begin{frame}{Idea.}
Hi.
\end{frame}

%\begin{frame}[allowframebreaks]{References}
%\bibliographystyle{abbrvnat}
%\bibliography{articles,proceedings,books,unpub}
%\end{frame}

>>>>

\title[Nonlinear system identification with neural networks for 
process control]{Nonlinear system identification with neural networks for 
process control}
\date{September 15, 2020}
\author[Kumar and Rawlings]{\large Pratyush Kumar and James B. Rawlings}
\institute[UCSB]{
	\begin{minipage}{4in}
		\vspace{-10pt}
		\centering
		\raisebox{-0.1\height}{\includegraphics[width=0.25\textwidth]{UCSB_seal}}
		%\hspace*{.2in}
		%\raisebox{-0.5\height}{\includegraphics[width=0.25\textwidth]{jci_logo}}
	\end{minipage}
	\vspace{10pt}
	\newline
	{\large Department of Chemical Engineering}
	\vspace{10pt}
	\newline
	{\large TWCCC Meeting (Virtual)}}
	%\vspace{10pt}
	%\newline
	%{\large Austin, TX}}

@@

% MPC intro frame
\begin{frame}{System identification for model predictive control (MPC)}

MPC requires a dynamic plant model ($x^+ = f(x, u)$) for use in online optimization.

	\begin{block}{Standard industrial practice}
		\begin{itemize}
			\item Estimate a linear model from data and use integrating disturbance models to maintain zero offset 
			in controlled measurements.
			\item For highly nonlinear plants, the closed-loop controller performance can deteriorate due to significant model mismatch. 
		\end{itemize}
	\end{block}

	\begin{block}{Neural networks and system identification\footnote[frame]{\cite{hussain:1999, draeger:engell:ranke:1995, prasad:bequette:2003, eaton:rawlings:ungar:1994, bhat:minderman:mcavoy:wang:1990}}}
		\begin{itemize}
			\item \textbf{Black-box identification:} Estimate the entire predictive model ($x^+ =  f(x, u)$) from actuators to
			sensors using the data collected from open-loop identification experiments.
			\item \textbf{Hybrid model identification:} Model the dynamics from actuators to sensors using first-principle knowledge, and use
			neural networks to estimate the mismatch or any unmeasured disturbance dynamics.  
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{Nonlinear HVAC example}
	\begin{align*}
	\dot{x} = Ax + Bg(u) + B_pp
	\end{align*}
	Nonlinearity between the valve (actuator) to the cooling duty. $x \in \{ T_{A1}, T_{C1}, T_{A2}, T_{C2} \}$, $u \in \{v_1, v_2\}$,
	and $p$ is the ambient temperature $T_a$ (disturbance).
	\pause
	\begin{figure}[!h]
		\centering
		\includegraphics[page = 5,width=0.6\textwidth]{plotshvacnn.pdf}
	\end{figure}
	\alert{Objective: Test the performance of linear MPC in regions of high plant-model mismatch.}
	\end{frame}

\begin{frame}{Linear MPC vs NN based MPC}
	\begin{figure}[!h]
		\centering
		\includegraphics[page = 2, width=0.48\textwidth]{plotshvacnn.pdf} \hfill
		\includegraphics[page = 3, width=0.48\textwidth]{plotshvacnn.pdf}
	\end{figure}

	\begin{itemize}
		\item NN trained on noisy open-loop system identification data (5000 samples).
		\item Change in ambient temperature at 10 hours, and setpoint changes in air-zone 
		temperatures at 50 and 100 hours. 
		\item The NN model provides superior closed-loop performance than the linear model.
	\end{itemize}
\end{frame}

	\begin{frame}{References}
\bibliographystyle{abbrvnat}
\bibliography{articles,proceedings,books,unpub}
\end{frame}
